An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-02-15 article/latex_files/ch5/5-1-ma2.tex
reordered files

\begin{figure}[ht]
  \centering
    \begin{minipage}[t]{.4\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Solve optimisation problems},
          xlabel={\(n_1\)},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.4\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Proposal regions},
          xlabel={\(n_1\)},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.4\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Sample},
          xlabel={\(n_1\)},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.4\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Evaluate posterior},
          xlabel={\(n_1\)},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \caption[Execution time exploiting parallelisation]{In the first
      line, we compare the parallel and sequential execution of the
      training part and at the second line the inference part. At the
      left figure, we measure the execution time for sampling \(n_2=50\)
      points per region. At the right figure we measure the execution
      time for evaluating the posterior at a batch of \(50\) points.}
      \label{fig:exec_parallel}
\end{figure}

>>>>

\begin{figure}[ht]
  \begin{center}
    \resizebox{.47\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/exec_time_solve.tex}
    }
    \resizebox{.49\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/exec_time_regions.tex}
    }
    \end{center}
    \caption[Execution time exploiting parallelisation]{In the first
      line, we compare the parallel and sequential execution of the
      training part and at the second line the inference part. At the
      left figure, we measure the execution time for sampling \(n_2=50\)
      points per region. At the right figure we measure the execution
      time for evaluating the posterior at a batch of \(50\) points.}
      \label{fig:exec_parallel}
\end{figure}

% \begin{figure}[ht]
%   \centering
%     \begin{minipage}[t]{.4\textwidth}
%       \begin{tikzpicture}
%         \begin{axis}[
%           title={Solve optimisation problems},
%           xlabel={\(n_1\)},
%           ylabel={seconds},
%           xmin=1, xmax=500,
%           ymin=0, ymax=7,
%           xtick={1,100,200,300,400,500},
%           ytick={0, 1, 2, 3, 4, 5, 6, 7},
%           legend pos=north west,
%           ymajorgrids=true,
%           grid style=dashed,
%           ]
%           \addplot[color=blue, mark=o] coordinates {
%             (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
%           };
%           \addlegendentry{sequential}
%           \addplot[color=red, mark=o] coordinates {
%             (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
%           };
%           \addlegendentry{parallel}          
%         \end{axis}
%       \end{tikzpicture}
%     \end{minipage}\hfill
%     \begin{minipage}[t]{.4\textwidth}
%       \begin{tikzpicture}
%         \begin{axis}[
%           title={Proposal regions},
%           xlabel={\(n_1\)},
%           ylabel={seconds},
%           xmin=1, xmax=500,
%           ymin=0, ymax=7,
%           xtick={1,100,200,300,400,500},
%           ytick={0, 1, 2, 3, 4, 5, 6, 7},
%           legend pos=north west,
%           ymajorgrids=true,
%           grid style=dashed,
%           ]
%           \addplot[color=blue, mark=o] coordinates {
%             (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
%           };
%           \addlegendentry{sequential}
%           \addplot[color=red, mark=o] coordinates {
%             (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
%           };
%           \addlegendentry{parallel}          
%         \end{axis}
%       \end{tikzpicture}
%     \end{minipage}\hfill
%     \begin{minipage}[t]{.4\textwidth}
%       \begin{tikzpicture}
%         \begin{axis}[
%           title={Sample},
%           xlabel={\(n_1\)},
%           ylabel={seconds},
%           xmin=1, xmax=500,
%           ymin=0, ymax=7,
%           xtick={1,100,200,300,400,500},
%           ytick={0, 1, 2, 3, 4, 5, 6, 7},
%           legend pos=north west,
%           ymajorgrids=true,
%           grid style=dashed,
%           ]
%           \addplot[color=blue, mark=o] coordinates {
%             (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
%           };
%           \addlegendentry{sequential}
%           \addplot[color=red, mark=o] coordinates {
%             (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
%           };
%           \addlegendentry{parallel}          
%         \end{axis}
%       \end{tikzpicture}
%     \end{minipage}\hfill
%     \begin{minipage}[t]{.4\textwidth}
%       \begin{tikzpicture}
%         \begin{axis}[
%           title={Evaluate posterior},
%           xlabel={\(n_1\)},
%           ylabel={seconds},
%           xmin=1, xmax=500,
%           ymin=0, ymax=7,
%           xtick={1,100,200,300,400,500},
%           ytick={0, 1, 2, 3, 4, 5, 6, 7},
%           legend pos=north west,
%           ymajorgrids=true,
%           grid style=dashed,
%           ]
%           \addplot[color=blue, mark=o] coordinates {
%             (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
%           };
%           \addlegendentry{sequential}
%           \addplot[color=red, mark=o] coordinates {
%             (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
%           };
%           \addlegendentry{parallel}          
%         \end{axis}
%       \end{tikzpicture}
%     \end{minipage}\hfill
%     \caption[Execution time exploiting parallelisation]{In the first
%       line, we compare the parallel and sequential execution of the
%       training part and at the second line the inference part. At the
%       left figure, we measure the execution time for sampling \(n_2=50\)
%       points per region. At the right figure we measure the execution
%       time for evaluating the posterior at a batch of \(50\) points.}
%       \label{fig:exec_parallel}
% \end{figure}

### 2022-02-15 article/latex_files/images/chapter4/mae2_hist_t2_romc.tex
reordered files

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.00551481774368941);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0605814218347914);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.168699423699822);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.340262186728983);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.48172967019454);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.661723210849365);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.926167683238105);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,1.1131441320768);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.19038558853121);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.39560413532974);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.38890799766854);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.45486223069012);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.89014334843844);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.80399178478282);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.15561058973456);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.33061276076321);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.24024442959031);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.34890403251458);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.31095726097247);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.33900171768764);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.07598627244674);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.71987564844275);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.65165022964706);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.40256222683377);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.18758980571923);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.0980208933351);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.803715750920935);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.742179116696122);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.678702875114039);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.583516431505742);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.398341719580722);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.257727424376927);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.229546935490747);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.210112717761985);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.129179090828181);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.0899034779939157);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0431810229330879);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.0479789143700981);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0287873486220588);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0143936743110293);

@@

0.0318388478807404 0
0.0318388478807404 3

@@

\addlegendentry{$\mu = 0.032$}

@@

-0.177435597378694 1
0.197481062716323 1

@@

\addlegendentry{$\sigma = 0.170$}

>>>>

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.0143830031521635);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0640495269335328);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.167967992034369);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.322416836713075);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.450460589062093);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.627682829295711);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.78449673556291);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,1.13618558747044);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.21557183831947);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.29143077400903);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.46122694206085);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.58740403775278);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.71596854606341);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.97590595810952);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.26932406129648);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.32343959220477);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.1892115171771);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.38168476397323);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.31304797611767);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.21128903529658);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.14821419761865);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.81725742398109);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.53374220971548);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.44383714928785);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.24606025648798);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.06408208570229);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.796495552018255);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.705157030158244);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.731994856866652);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.533344891350605);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.478183009636268);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.277899805953886);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.198597889919886);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.151665334936985);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.131771535511397);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.0942116661455654);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0673572489817432);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.0288673924207473);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0336786244908719);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0144336962103735);

@@

0.0325240508501527 0
0.0325240508501527 3

@@

\addlegendentry{$\mu = 0.033$}

@@

-0.175528279454964 1
0.1970811913253 1

@@

\addlegendentry{$\sigma = 0.169$}

### 2022-02-15 article/latex_files/images/chapter4/mae2_hist_t2_romc_bo.tex
reordered files

title={ROMC (gradient-based) - \(\displaystyle \theta_2\)},

@@

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.0143830031521635);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0640495269335328);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.167967992034369);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.322416836713075);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.450460589062093);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.627682829295711);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.78449673556291);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,1.13618558747044);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.21557183831947);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.29143077400903);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.46122694206085);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.58740403775278);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.71596854606341);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.97590595810952);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.26932406129648);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.32343959220477);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.1892115171771);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.38168476397323);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.31304797611767);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.21128903529658);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.14821419761865);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.81725742398109);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.53374220971548);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.44383714928785);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.24606025648798);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.06408208570229);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.796495552018255);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.705157030158244);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.731994856866652);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.533344891350605);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.478183009636268);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.277899805953886);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.198597889919886);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.151665334936985);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.131771535511397);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.0942116661455654);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0673572489817432);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.0288673924207473);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0336786244908719);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0144336962103735);

@@

0.0325240508501527 0
0.0325240508501527 3

@@

\addlegendentry{$\mu = 0.033$}

@@

-0.175528279454964 1
0.1970811913253 1

@@

\addlegendentry{$\sigma = 0.169$}

>>>>

title={ROMC (BO) - \(\displaystyle \theta_2\)},

@@

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.0617545870506399);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.494036696405118);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.308772935253199);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,0.864564218708957);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.11158256691152);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,0.802809631658317);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.49395771225155);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.71306067268783);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.17926096548025);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.06759941441516);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,1.5396445345721);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,1.91609586839403);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,1.79258669429275);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,1.59403798219366);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,1.58667684276459);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,1.52979906798699);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.15183142210051);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,2.06111444803853);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.47292129320938);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.85529643854941);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.86505006309548);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,2.67369166423286);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,1.96552066170352);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,1.29148734508544);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,1.68849292724457);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,1.00470598608042);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.703294190256297);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.703294190256294);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,1.2056471832965);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.200941197216084);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.100470598608042);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0);

@@

0.100012161271839 0
0.100012161271839 3

@@

\addlegendentry{$\mu = 0.100$}

@@

-0.108452084584719 1
0.278478839382765 1

@@

\addlegendentry{$\sigma = 0.176$}
